---
title: "Combined"
author: "Maxwel Coura Oliveira"
date: "5/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	fig.align = "center",
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	include = FALSE
)
```





```{r message = FALSE}
# Packages
library(gt)
library(RColorBrewer)
library(CircStats)
library(openair)
library(scales)
library(tidyverse)
library(lme4)
library(emmeans)
library(ggpmisc)
library(lmerTest)
library(multcomp)
library(cowplot)
library(patchwork)
library(multcomp)
library(ggtext)
library(ggeffects)
options(scipen = 999)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Playfair Display", ## name of Google font
                "Playfair")  ## name that will be used in R
font_add_google("Bangers", "Bangers")
font_add_google("Schoolbell", "bell")
font_add_google("Fredoka One", "fredoka")
font_add_google("Lobster", "lobster")
font_add_google("Indie Flower" , "flower")
font_add_google("Roboto Condensed", "roboto")
```



Here is presented ANOVA results (upwind, inswath, AUC) with 5% significance level, and figures from downwind deposition.


```{r load-data}
## Load deposition dataset
#missouri
path_mo <- "./data/deposition/Deposition data_MO.xlsx"

missouri <- path_mo %>% 
  readxl::excel_sheets() %>% 
  set_names(c("downwind_mo", "upwind_mo", "inswath_mo")) %>% 
  map(readxl::read_excel, path = path_mo)



downwind_mo <- missouri$downwind_mo %>% 
  mutate(type = "downwind")
upwind_mo <- missouri$upwind_mo %>% 
  mutate('distance (m)' = NA,
         type = "upwind")
inswath_mo <- missouri$inswath_mo %>%
  mutate('distance (m)' = NA,
         type = "inswath") %>% 
  dplyr::select(-...8)

missouri <- downwind_mo %>% 
  bind_rows(upwind_mo) %>% 
  bind_rows(inswath_mo) %>% 
  mutate(location = "missouri")


#nebraska
path_ne <- "./data/deposition/Deposition data_NE.xlsx"

nebraska <- path_ne %>% 
  readxl::excel_sheets() %>% 
  set_names(c("downwind_ne", "upwind_ne", "inswath_ne")) %>% 
  map(readxl::read_excel, path = path_ne)



downwind_ne <- nebraska$downwind_ne %>% 
  mutate(type = "downwind")
upwind_ne <- nebraska$upwind_ne %>% 
  mutate('distance (m)' = NA,
         type = "upwind")
inswath_ne <- nebraska$inswath_ne %>%
  mutate('distance (m)' = NA,
         type = "inswath")

nebraska <- downwind_ne %>% 
  bind_rows(upwind_ne) %>% 
  bind_rows(inswath_ne) %>% 
  mutate(location = "nebraska")


#wisconsin
path_wi <- "./data/deposition/Deposition data_WI.xlsx"

wisconsin <- path_wi %>% 
  readxl::excel_sheets() %>% 
  set_names(c("downwind_wi", "upwind_wi", "inswath_wi")) %>% 
  map(readxl::read_excel, path = path_wi)



downwind_wi <- wisconsin$downwind_wi %>% 
  mutate(type = "downwind")
upwind_wi <- wisconsin$upwind_wi %>% 
  mutate('distance (m)' = NA,
         type = "upwind")
inswath_wi <- wisconsin$inswath_wi %>%
  mutate('distance (m)' = NA,
         type = "inswath")

wisconsin <- downwind_wi %>% 
  bind_rows(upwind_wi) %>% 
  bind_rows(inswath_wi) %>% 
  mutate(location = "wisconsin")
```


```{r join-data}
### Join location datasets
new_dt <- missouri %>% 
  bind_rows(nebraska) %>% 
  bind_rows(wisconsin) %>% 
  janitor::clean_names() %>% 
  rename(deposition = n_l_cm2) %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(block = as_factor(block)) %>% 
  mutate(distance_m = replace_na(distance_m, 0)) %>% 
  mutate(distance_log = log10(distance_m),
         deposition_log = log10(deposition)) 
```


## Deposition inswath 



```{r}
### Filter deposition dataset inswath
inswath <-  new_dt %>% 
  filter(type == "inswath")
```


```{r}
### Test ANOVA assumptions
#### Normal distribution
inswath %>% 
  ggplot(aes(x = deposition)) +
  geom_histogram()
# data has normal distribution
```



```{r}
#### Homogeneity of variances
bartlett.test(deposition ~ location, data = inswath)
# can't compare locations
```




```{r}
### Data analysis
#### Model
model1 <- lmer(deposition ~  solution * sprayer * nozzle +
                (1|block/location), 
              REML = FALSE, data = inswath)
```



```{r}
#### Checking normality
par(mfrow = c(1,2))  # This code put two plots in the same window
#hist(model$residuals)   # Makes histogram of residuals  
plot(model1, which = 2)   # Makes Q-Q plot
```





```{r}
#### Fit models and ANOVA
anova(model1)
```



### Solution x sprayer 

```{r}
#### Solution x sprayer 
lsmeans1 <- emmeans(model1, ~ solution * sprayer, cont="pairwise", 
                      adjust="none", alpha=0.05)

cld1 <- cld(lsmeans1$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld1
```
```{r echo=FALSE, include=TRUE}
cld1 %>% 
  tibble() %>% 
  rename(deposition = emmean) %>% 
  mutate_if(is.double, ~ round(., 1)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("Spray solution deposition inswath"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Solution x sprayer averaged across nozzle"))
```


### Solution x nozzle

```{r}
#### Solution x sprayer 
lsmeans2 <- emmeans(model1, ~ solution * nozzle, cont="pairwise", 
                      adjust="none", alpha=0.05)

cld2 <- cld(lsmeans2$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld2
```

```{r echo=FALSE, include=TRUE}
cld2 %>% 
  tibble() %>% 
  rename(deposition = emmean) %>% 
  mutate_if(is.double, ~ round(., 1)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("Spray solution deposition inswath"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Solution x nozzle averaged across srayer"))
```




## Deposition upwind 



```{r}
### Filter deposition dataset upwind
upwind <- new_dt %>% 
  filter(type == "upwind")
```



```{r}
### Test ANOVA assumptions
#### Normal distribution
upwind %>% 
  ggplot(aes(x = deposition)) +
  geom_histogram() 
# not normalized
```



```{r}
##### Log scale
upwind %>% 
  ggplot(aes(x = log(deposition))) +
  geom_histogram()
# yes!
```



```{r}
#### Homogeneity of variances
bartlett.test(deposition ~ location, data = upwind)
# can't compare locations
```




```{r}
#### Model
model2 <- lmer(log(deposition) ~ solution * sprayer * nozzle + (1|block/location), 
              REML = FALSE, data = upwind)
```


```{r}
# Checking normality
par(mfrow = c(1,2))  # This code put two plots in the same window
#hist(frogs_anova$residuals)   # Makes histogram of residuals  
plot(model2, which = 2)   # Makes Q-Q plot
```





```{r}
#### ANOVA 
anova(model2) 
```



```{r}
#### Solution
lsmeans3 <- emmeans(model2, ~ solution, cont="pairwise", type = "response",
                      adjust="none", alpha=0.05)

cld3 <- cld(lsmeans3$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld3
```

### Solution

```{r echo=FALSE, include=TRUE}
cld3 %>% 
  tibble() %>% 
  rename(deposition = response) %>% 
  mutate_if(is.double, ~ round(., 2)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("Spray solution deposition upwind"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Solution is averaged across sprayer and nozzle"))
```



# Deposition downwind 





```{r}
## Filter data
data_dw <- new_dt %>% 
  filter(type == "downwind") %>% 
  mutate(pass = factor(pass)) %>% 
  group_by(location, pass, block) 
```





```{r}
## Visualize
data_dw %>% 
  ggplot(aes(x = distance_m, y = deposition, color = nozzle)) +
  geom_point() +
  facet_grid(~ location)
# some trt have rapid decrease and some trt have linear trend
```





```{r}
## Visualize (log scale)
data_dw %>% 
#  unite("trt", c("solution", "sprayer", "nozzle")) %>% 
  ggplot(aes(x = log(distance_m), y = log(deposition), color = nozzle)) +
  geom_point() +
  facet_grid(sprayer ~ solution) +
  geom_smooth(method = "lm") 
# better go with log scale
```



```{r}
## Normal distribution
data_dw %>% 
  ggplot(aes(x = log(deposition))) +
  geom_histogram()
```


```{r}
# Linear Model
## Arrange dataset
data_dw1 <- data_dw %>% 
  group_by(solution, sprayer, nozzle) %>% 
  nest()

data_dw1
```



```{r}
### Model function
model3 <- function(df){
  lmer(log(deposition) ~ log(distance_m) + 
         (1|block/location), REML = TRUE, data = df)
}
```



```{r warning=FALSE, message = FALSE}
### Fit model and confidence intervals
data_dw2 <- data_dw1 %>% 
  mutate(model = map(data, model3),
         summary = map(model, broom.mixed::tidy),
         confint = map(model, confint))
```




```{r}
### Get parameters from models
params <- data_dw2 %>% 
  unnest(summary) %>% 
  filter(effect == "fixed") %>% 
  mutate(estimate_exp = exp(estimate),
         estimate_exp = case_when(
           term == "log(distance_m)" ~ -estimate_exp,
           TRUE                      ~ estimate_exp
         )) %>% 
  dplyr::select(solution, sprayer, nozzle, term, estimate, std.error, statistic, p.value, estimate_exp) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  mutate(term = fct_recode(term,
                           slope = "log(distance_m)"),
         term = fct_recode(term,
                           Intercept = "(Intercept)")) %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), sep = " ", remove = FALSE)

params
```






```{r}
### Get confidence intervals
get_cis <- function(number){
  exp(data_dw2$confint[[number]]) %>%
    as_tibble() %>%
    slice_tail(n=2)
} 

number <- as_tibble(c(1:12))

intervals <- number %>%
  mutate(interval = map(value, get_cis)) %>%
  unnest(interval)

# join to main dataset
downwind_final <- params %>%
  bind_cols(intervals) %>%
  rename(lower = `2.5 %`,
         upper = `97.5 %`) %>%
  mutate(lower = case_when(
           term == "log(distance_m)" ~ -lower,
         TRUE                        ~ lower
         ),
         upper = case_when(
           term == "log(distance_m)" ~ -upper,
         TRUE                        ~ upper,
         )) %>% 
  mutate(across(where(is_double), round, 3))
```




```{r}
## Distance of deposition at 0
distance_final <- downwind_final %>% 
  dplyr::select(trt, term, estimate_exp) %>% 
  pivot_wider(
              names_from = term, 
              values_from = estimate_exp) 
```


```{r}
distance_function <- function(int, slope, y = 0) {
  distance = (y - int) / slope
  return(distance)
}

distance_final1 <- distance_final %>% 
  mutate(distance_m = map2_dbl(Intercept, slope, distance_function),
         distance_m = round(distance_m, 10)) %>% 
  mutate( y = Intercept + slope * distance_m)
```





```{r}
## Predict
downwind_final1 <- downwind_final %>% 
  pivot_wider(id_cols = trt:nozzle,
              names_from = term, 
              values_from = estimate_exp) 
```


```{r}
linear <- function(a, b, d) {
  y = a + b*d
  return(y)
}

linear(distance_final1$Intercept, distance_final1$slope, distance_final1$distance_m)
```

### Intercept

```{r include=TRUE}
a <- downwind_final %>% 
  filter(term == "Intercept") %>% 
    mutate(trt = factor(trt, levels = c(
    "Intact Hood TTI", "Intact Hood ULD", "Water Hood TTI",
    "Intact Hood AIXR", "Water Hood AIXR", "Water Hood ULD",
    "Intact Open TTI", "Water Open TTI", "Intact Open ULD",
    "Water Open ULD", "Water Open AIXR", "Intact Open AIXR"
  ))) %>% 
  ggplot(aes(x = reorder(trt, estimate_exp), y = estimate_exp, color = trt)) +
  geom_point(size = 2, stroke = 1) +
  scale_color_brewer(palette = "Paired") +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.5) +
  coord_flip() +
  geom_text(aes(x = 1.5, y = 15,
                label = "Lower values lower spray \nparticle deposition"),
            stat = "unique", family = "bell",
            size = 4, color = "darkcyan") +
  labs(title = "Intercept at downwind", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")")), x = "") +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(family = "fredoka", color = "#282728")) 
a
```

### Slope

```{r include=TRUE}
b <- downwind_final %>% 
  filter(term == "slope") %>% 
  mutate(trt = factor(trt, levels = c(
    "Intact Hood TTI", "Intact Hood ULD", "Water Hood TTI",
    "Intact Hood AIXR", "Water Hood AIXR", "Water Hood ULD",
    "Intact Open TTI", "Water Open TTI", "Intact Open ULD",
    "Water Open ULD", "Water Open AIXR", "Intact Open AIXR"
  ))) %>% 
  ggplot(aes(x = reorder(trt, estimate_exp), y = estimate_exp, color = trt)) +
  geom_point(size = 2, stroke = 1) +
  scale_color_brewer(palette = "Paired") +
  geom_linerange(aes(ymin = -lower, ymax = -upper), size = 1.5) +
  coord_flip() +
  geom_text(aes(x = 11.6, y = -0.43,
                label = "Higher values lower spray \nparticle deposition rate"),
            stat = "unique", family = "bell",
            size = 4, color = "darkcyan") +
  labs(title = "Slope at downwind", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")")), x = "") +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(family = "fredoka", color = "#282728")) 
b
```

### Predicted downwind distance

```{r include=TRUE}
c <- distance_final1 %>% 
    mutate(trt = factor(trt, levels = c(
    "Intact Hood TTI", "Intact Hood ULD", "Water Hood TTI",
    "Intact Hood AIXR", "Water Hood AIXR", "Water Hood ULD",
    "Intact Open TTI", "Water Open TTI", "Intact Open ULD",
    "Water Open ULD", "Water Open AIXR", "Intact Open AIXR"
  ))) %>% 
  ggplot(aes(x = reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, fill = trt)) +
  geom_bar(stat = "identity", width = 0.8) +
  coord_flip() +
  geom_label(aes(label = round(distance_m, 0)), size = 3) +
  scale_fill_brewer(palette = "Paired") +
  labs(title = "Predicted downwind distance (m)", 
       y = "", x = "") +
#  geom_label(aes(label = distance_0)) +
  ylim(0,60) +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(family = "fredoka", size = 12, color = "#282728"),
        panel.background = element_rect(fill = "#F5F5F5", color = NA),
        axis.text.x = element_blank(),
        axis.text = element_markdown(size = 8),
        axis.ticks.x = element_blank()) +
   geom_text(x = 4, y = 35,
                label = "Distance where \nno spray \nparticle \ndeposition \nwas detected",
            stat = "unique", family = "flower",
            size = 4, color = "darkcyan") 
c
```


```{r}
fig <- data_dw2 %>% 
  dplyr::select(solution, sprayer, nozzle, model)
```


```{r warning=FALSE, message = FALSE}
fig_model <- function(model){
  ggpredict(model, terms = "distance_m", back.transform = TRUE) %>% 
    as_tibble()
}

fig1 <- fig %>% 
  mutate(estimates = map(model, fig_model)) %>% 
  unnest(estimates) %>% 
  rename(distance_m = x) %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), sep = " ") %>% 
  mutate_if(is_character, as_factor) 
```

```{r}
label <- distance_final %>% 
  mutate(Intercept = round(Intercept, 1),
         slope = round(slope, 2)) %>% 
  mutate(y = "y = ",
         x = "x") %>% 
  unite("formula", c("y", "Intercept", "slope"), sep = " ") %>% 
  unite("formula", c("formula", "x"), sep = "")
```


```{r}
fig2 <- fig1 %>% 
  left_join(label)
```
 
### Back-transformed linear models

```{r include=TRUE}
figs <- fig2 %>% 
  mutate(trt = factor(trt, levels = c(
    "Intact Hood TTI", "Intact Hood ULD", "Intact Hood AIXR",
    "Water Hood TTI",  "Water Hood ULD", "Water Hood AIXR",
    "Intact Open TTI", "Water Open TTI", "Intact Open ULD",
    "Water Open ULD", "Water Open AIXR", "Intact Open AIXR"
  ))) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula)) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
#  geom_segment(aes(x = 33.5, y = 0, xend = 33.5, yend = 15)) +
  facet_wrap(~ trt, ncol = 4) +
  theme_test() +
#  background_grid() +
  theme(legend.position = "none") +
  geom_label(aes(label = formula), x = 30, y = 20, color = 1) +
  labs(title = "Back-transformed linear models prediction of spray particle deposition",
    x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        panel.background = element_rect(fill = "#F5F5F5", color = NA),
        plot.title = element_markdown(family = "fredoka", size = 12, color = "#282728"),
        strip.text = element_textbox(
          size = 12,
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3))) +
  ggsave("linear_combined.png")
figs
```





### AUC 


```{r}
(id_df <- data_dw %>% 
  distinct(pass, block, location) %>% 
  ungroup() %>% 
  mutate(id = as_factor(dplyr::row_number()))
)
```

```{r}
id_df1 <- data_dw %>% 
  left_join(id_df) 
```


```{r}
auc_cal <- function(number){
  df <- id_df1 %>% 
    filter(id == number)  
  
  audps(df$deposition, df$distance_m, type="absolute") 
}

auc_data <- id_df1 %>% 
  group_by(id) %>% 
  nest() %>% 
  mutate(auc = map_dbl(id, auc_cal)) %>% 
  ungroup(id) %>% 
  unnest() 
```

```{r}
auc_data1 <- auc_data %>% 
  filter(distance_m == 1)
```

```{r}
auc_data1 %>% 
  ggplot(aes(x = log(auc))) + 
  geom_histogram()
```


```{r}
auc_data2 <- auc_data1 %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), sep = " ", remove = FALSE)
```


```{r}
auc_model <- lmer(log(auc) ~ solution * sprayer * nozzle + (1|block/location), data=auc_data2)
```


```{r}
# Checking normality
par(mfrow = c(1,2))  # This code put two plots in the same window
#hist(auc_model$residuals)   # Makes histogram of residuals  
plot(auc_model, which = 2)   # Makes Q-Q plot
```






```{r}
anova(auc_model)
```


### Solution x sprayer 

```{r}
lsmeans4 <- emmeans(auc_model, ~  solution * sprayer, cont="pairwise", type = "response",
                      adjust="none", alpha=0.05)

cld4 <- cld(lsmeans4$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE,
            type = "response")
cld4
```

```{r, include=TRUE}
cld4 %>% 
  tibble() %>% 
  rename(deposition = response) %>% 
  mutate_if(is.double, ~ round(., 1)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("AUC for spray solution deposition downwind"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Solution x sprayer averaged across nozzle"))
```



### Nozzle x sprayer

```{r}
lsmeans5 <- emmeans(auc_model, ~  nozzle * sprayer, cont="pairwise", 
                      adjust="none", alpha=0.05, type = "response")

cld5 <- cld(lsmeans5$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld5
```

```{r, include=TRUE}
cld5 %>% 
  tibble() %>% 
  rename(deposition = response) %>% 
  mutate_if(is.double, ~ round(., 1)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("AUC for spray solution deposition downwind"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Nozzle x sprayer averaged across solution"))
```

###  Solution x nozzle

```{r}
lsmeans6 <- emmeans(auc_model, ~  nozzle * solution, cont="pairwise", 
                      adjust="none", alpha=0.05, type = "response")

cld6 <- cld(lsmeans6$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
cld6
```

```{r, include=TRUE}
cld6 %>% 
  tibble() %>% 
  rename(deposition = response) %>% 
  mutate_if(is.double, ~ round(., 1)) %>% 
  dplyr::select(-df) %>% 
  gt() %>% 
  tab_header(
    title = md("AUC for spray solution deposition downwind"),
    subtitle = "Data is combined across Nebraska, Missouri and Wisconsin"
  ) %>%
  tab_source_note(md("Solution x nozzle averaged across sprayer"))
```


```{r}
library(webshot)
# R Markdown file
input_file <- system.file("combined.Rmd", package = "knitr")
rmdshot(input_file, "minimal_rmd.png")
```

